Limited plasticity but increased variance in physiological rates across ectotherm populations under climate change

### 2024-12-17 ms.qmd
Data now should be organised for new analysis but secies names are off because used wide dtaa and probably we only cleaned up species names in wide data. S=Need to fix this for phylogenetic tree

>>>>

```{r, wildlnRR_acutevsacclim}
#| label: wildlnRR_acutevsacclim
#| echo: false
#| include: false

###---------------------------------------###
# Analysis that calculates the plastic adjustment, acclimation - acute within a study and trait to look at whether plasticity is correlated with climate. A good point raised by Reviewer 1 that we should test.
###---------------------------------------###

###---------------------------------------###
# Data
###---------------------------------------###

  # Create a match column.
  climate2 <- climate %>% 
              mutate(match = paste(Species, Latitude, Longitude, sep =".")) %>% 
              dplyr::select(Species, Latitude, Longitude, match, cv, sd, mean, acf_lag1, acf_all)

  # Subset the data and do some new calculations
    # Steps:
    # 1. Suse wide data
    # 2. Drop out lnVR and lnCVR
    # 3.  Exclude effects where we don't have BOTH acute and acclimation. We need both to subtract from each other
    # 4. Calculate the weighted average of the effects and its associated sampleing variance so we have only a single acute
    # 5. Clean up by removing old acute columns
    # 6. Calculate the difference between acclimation and acute and it's associated associated sampling variance
    # 7. Clean up by removing old acclimation and acute columns as well as all 'r' columns
    # 8. Add a match column for joining climate data

                          drop <- colnames(data_wide)[grep("ln[CV]", colnames(data_wide))]

  lnRRQ10_data_acc_minus_aclim <- data_wide %>%        
                  dplyr::select(!all_of(drop)) %>%  
                  filter(!is.na(lnRR_Q10_acute_t1) | !is.na(lnRR_Q10_acute_t2)) %>% 
                  mutate(lnRR_acute = weighted_avg_effects(lnRR_Q10_acute_t1, lnRR_Q10_acute_t2, V_lnRR_Q10_acute_t1, V_lnRR_Q10_acute_t2),
                      lnRR_acute_SV = weighted_avg_sv(V_lnRR_Q10_acute_t1, V_lnRR_Q10_acute_t2))   %>% 
                  dplyr::select(-lnRR_Q10_acute_t1, -lnRR_Q10_acute_t2, -V_lnRR_Q10_acute_t1, -V_lnRR_Q10_acute_t2)  %>% 
                  mutate(lnRRQ10_ac_acclimate = lnRR_acute - lnRR_Q10_acclim, 
                         lnRRQ10_ac_acclimate_SV = lnRR_acute_SV + V_lnRR_Q10_acclim) %>%
                  dplyr::select(-lnRR_Q10_acclim, -V_lnRR_Q10_acclim, -lnRR_acute_SV, -lnRR_acute, -grep("r", colnames(.)))  %>% 
                  mutate(match = paste(gsub("_", "", species_full), lat, long, sep = "."), 
                    max_temp_c = scale(temp_2, scale = FALSE))

# Now that we have the data calcualted as the difference between acute and acclimation for each effect we want to know of this difference, i.e., the direction and magnitude of plasticity is associated with climate. We do not need to pivot longer because the response is simply the difference now so we are ready for anlaysis

# Now, join climate data to full data. This will give us all the climate variability data for each site across time
lnRRQ10_data_wild_acute_vs_acclim <- left_join(lnRRQ10_data_acc_minus_aclim, climate2, by = "match")

# Check and prune tree
tree_lnrr_wild <- tree_checks(data = lnRRQ10_data_wild_acute_vs_acclim, tree = tree_p0.7, dataCol = "species_full", type = "prune")
tree_checks(data = lnRRQ10_data_wild_acute_vs_acclim, tree = tree_lnrr, dataCol = "species_full", type = "check") # Good
